---
title: "Introduction to Lubridate and Forcats Package in R"
subtitle: 
author: 
  - "Oluwafemi Oyedele"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css]
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

# Lubridate Package in R

- Yesterday we did a few functions on the lubridate package and I said that the lubridate package is used for manipulating date in R.

- I said that the lubridate package is not part of the core tidyverse package that is why we have to install it and load it seperately.

- We saw that there are three ways in which we can create a date/time using the lubridate package.

1) We can create a date/time from a strings

ymd('2022-01-31')

mdy('01-31-2022')

N/B: this function also takes unquoted numbers

ymd(20220131)


2) We can create a date/time from individual date-time components as we can see in the flight dataset where we have to usethe make_date and make_datetime to create a datetime.
---
flights %>% 
select(year,month,day,hour,minute) %>% 
mutate(Departure=make_datetime(year,month,day,hour,minute))


3) We also create a date from an existing date/time objects
 This is very useful if you want to switch from one date fromat to another e.g.
 
 as_datetime(today())
 
 # We also look at some accessor functions 
 mday()
 
 year()
 
 wday()
---
- In R when we subtract two date we get a difftime object
# How old is Buhari?


Age <- today()-ymd(19791014)

- A difftime object records a time span of seconds, minutes, hours, days, or weeks which makes it a little difficult to work with.

- We can overcome this with the function below

as_duration (Age)

---
Assignment

1) What happens if you parse a string that contains invalid dates?

2) What does the tzone argument to today() do? Why is it important?


---
# Introduction to Forcats Package in R

- In R factors are used to work with categorical variables, variables that have a fixed and known set of possible values.
- We will be working with the gss_cat data set from the forcats package.
- When factors are stored in a tibble the best way to view them is to use the count function or to visualize them using a bar chart e.g.

gss_cat %>% 
count(race)

# The functions we will be looking at are:
1) fct_reorder and fct_reorder2: This reorder factor levels by sorting along another variable

2) fct_recode: This is used to recode factor levels by hand

3) fct_colapse: This is used to collapse factor levels into manually defined groups





###########################################################################
###########################################################################
###                                                                     ###
###                           FORCATS PACKAGE                           ###
###                                                                     ###
###########################################################################
###########################################################################


library(tidyverse)

head(gss_cat)

gss_cat %>% 
count(partyid)

# fct_reorder function
gss_cat1 =gss_cat %>% 
mutate(tvhours=mean(tvhours,n=n()))

fct_reorder <- gss_cat1 %>% mutate(partyid=fct_reorder(partyid,tvhours))

ggplot(fct_reorder,aes(x=partyid,y=tvhours))+geom_line()

# FCT_Reorder2
ggplot(data=gss_cat,mapping=aes(x=tvhours,color=relig,fct_reorder2(marital,relig,tvhours)))+geom_line()


# fct_recode

gss=gss_cat %>% 
mutate(partyid=fct_recode(partyid,"Dont know"="Don't know","Not strong republican"="Not str republican","Independent near republican"="Ind,near rep","Not strong democrat"="Not str democrat"))

# fct_colapse
gss2=gss_cat %>% 
mutate(partyid=fct_collapse(partyid,ADP=c("No answer","Don't know","Other party","Strong republican"),APC=c("Not str republican","Ind,near rep","Independent"),PDP=c("Ind,near dem","Not str democrat","Strong democrat")))



############################################################################
############################################################################
###                                                                      ###
###                              ASSINGMENT                              ###
###                                                                      ###
############################################################################
############################################################################


1) apply the recode and collapse function to the the marital column from the gss_cat dataset
