---
title: Scientific Writting in R
author:
  - name: Fatimah 
    email: alice@example.com
    affiliation: IITA
    correspondingauthor: true
    footnote: 1
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
  - name: Cat Memes
    email: cat@example.com
    affiliation: Another University
    footnote: 2
  - name: Derek Zoolander
    email: derek@example.com
    affiliation: Some Institute of Technology
    footnote: 2
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "This "
  - code: 2
    text: "Another author footnote."
abstract: |
  This is the abstract.
  Purpose: Although litter decomposition and nutrient release patterns have been studied in cocoa agroforestry systems in general, studies focusing on organic and conventional cocoa systems are lacking which is critical as organic farms are particularly dependent on  nutrient return from decomposing litter.

keywords: 
  - Litter decomposition
  - Litterfall
journal: "An awesome journal"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: false
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---

# Introduction
Yam production in Nigeria is one of the largest agricultural produce [@pérez-flores2017a]. Knowing the nutrient composition of litter is useful for planning nutrient management of plantations [@bai2022leaf]. In Cocoa (Theobroma cacao L.) plantations, tree species are combined in different vertical strata [@fontes2014nutrient; @pérez-flores2017a;@Dirac1953888;@Feynman1963118]. Cocoa litter has a poor quality @fontes2014nutrient reported N rate in cocoa litter was low .

The objectives of this work is to identify the socio-economy characteristics of the farmers.






# Materials and Method
## Study area

The study was conducted in the ejido Miguel Hi dalgo. Climate is hot and wet abundant rain in summer.

```{r,Map,echo=FALSE,message=FALSE,warning=FALSE}
library(leaflet)

leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = 4.201,lat = 7.234)
```
The experiment was a factorial laid out in a RCBD with three replicates.


# Statistical analysis

The data collected was analyzed using analysis of variance (ANOVA) and significantly different means were seperated using Tukey's HSD at (P<0.05).




# Result


```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.cap='plot1'}
library(ggplot2)
ggplot(data=iris,aes(x=Sepal.Length,y=Sepal.Width))+geom_point()+
  geom_smooth()
```

# Discussion

The traders were selling agricultural produce for the farmers. 50% of the traders were female, 30% were teachers and 20% were farmers which shows that majority of the female living in the community were traders (Table 1) [@adebayo2020assessment].

According to plot1 the Sepal length has a strong negative relationship with Sepal Width.

# Conclusion

It is concluded that majority of the female traders focus more on agricultural produce.

# Acknowledgement

I am pleased to appreciate Prof Fatimah from University of Ibadan Nigeria for assisting me throughout the computation of this manuscript. I appreciate Dr Mr Femi for all hard work in encouraging me throughout the research.


# References {-}

