---
title: "Tidyverse"
subtitle: "Forcats and Stringr Package"
author: "Oluwafemi Oyedele"
institute: 
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: ['default',"uio","uio-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Lubridate Package in R

- Yesterday we did a few functions on the lubridate package and I said that the lubridate package is used for manipulating date in R.

- I said that the lubridate package is not part of the core tidyverse package that is why we have to install it and load it seperately.

- We saw that there are three ways in which we can create a date/time using the lubridate package.

1) We can create a date/time from a strings

```{r, load}
library(tidyverse)
library(lubridate)
library(nycflights13)
```

```{r}

ymd('2022-01-31')

mdy('01-31-2022')

```
N/B: this function also takes unquoted numbers
```{r}
ymd(20220131)
```



2) We can create a date/time from individual date-time components as we can see in the flight dataset where we have to usethe make_date and make_datetime to create a datetime.
---
```{r}
flights %>% 
select(year,month,day,hour,minute) %>% 
mutate(Departure=make_datetime(year,month,day,hour,minute))
```


3) We also create a date from an existing date/time objects
 This is very useful if you want to switch from one date fromat to another e.g.
 
 
```{r}
 as_datetime(today())
```
 
 
 # We also look at some accessor functions 
 mday()
 
 year()
 
 wday()
---
- In R when we subtract two date we get a difftime object
# How old is Buhari?



```{r}
Age <- today()-ymd(19791014)

```


- A difftime object records a time span of seconds, minutes, hours, days, or weeks which makes it a little difficult to work with.

- We can overcome this with the function below

as_duration (Age)

---
Assignment

1) What happens if you parse a string that contains invalid dates?

2) What does the tzone argument to today() do? Why is it important?


---
# Introduction to Forcats Package in R

- In R factors are used to work with categorical variables, variables that have a fixed and known set of possible values.
- We will be working with the gss_cat data set from the forcats package.
- When factors are stored in a tibble the best way to view them is to use the count function or to visualize them using a bar chart e.g.


```{r}
gss_cat %>% 
count(race)

```
---
# The functions we will be looking at are:
1) fct_reorder and fct_reorder2: This reorder factor levels by sorting along another variable

2) fct_recode: This is used to recode factor levels by hand

3) fct_colapse: This is used to collapse factor levels into manually defined groups





###########################################################################
###########################################################################
###                                                                     ###
###                           FORCATS PACKAGE                           ###
###                                                                     ###
###########################################################################
###########################################################################


```{r}

library(tidyverse)

head(gss_cat)

gss_cat %>% 
count(partyid)

```

# fct_reorder function
```{r}
gss_cat1 =gss_cat %>% 
mutate(tvhours=mean(tvhours,n=n()))

```

```{r}
fct_reorder <- gss_cat1 %>% mutate(partyid=fct_reorder(partyid,tvhours))

```

```{r}
ggplot(fct_reorder,aes(x=partyid,y=tvhours))+geom_line()

```


# FCT_Reorder2

```{r}
ggplot(data=gss_cat,mapping=aes(x=tvhours,color=relig,fct_reorder2(marital,relig,tvhours)))+geom_line()
```
---

- fct_recode


```{r}
gss=gss_cat %>% 
mutate(partyid=fct_recode(partyid,"Dont know"="Don't know","Not strong republican"="Not str republican","Independent near republican"="Ind,near rep","Not strong democrat"="Not str democrat"))
```


- fct_colapse

```{r}
gss2=gss_cat %>% 
mutate(partyid=fct_collapse(partyid,ADP=c("No answer","Don't know","Other party","Strong republican"),APC=c("Not str republican","Ind,near rep","Independent"),PDP=c("Ind,near dem","Not str democrat","Strong democrat")))
```


---
############################################################################
############################################################################
###                                                                      ###
###                              ASSINGMENT                              ###
###                                                                      ###
############################################################################
############################################################################

- Assignment

#  apply the recode and collapse function to the the marital column from the gss_cat dataset
