---
title: "Report Writting in R"
author: "Oluwafemi Oyedele"
date: '2022-03-10'
output:
  word_document: default
  html_document: default
bibliography: references.bib
---

# Abstract

# Introduction

Yam production in Nigeria is one of the largest agricultural produce [@pérez-flores2017a]. Knowing the nutrient composition of litter is useful for planning nutrient management of plantations [@bai2022leaf]. In Cocoa (*Theobroma* cacao\* L.) plantations, tree species are combined in different vertical strata [@fontes2014nutrient; @pérez-flores2017a]. Cocoa litter has a poor quality @fontes2014nutrient reported N rate in cocoa litter was low .

The objectives of this work is to identify the socio-economy characteristics of the farmers.

# Materials and Methods

Study area

The study was conducted in the ejido Miguel Hi dalgo. Climate is hot and wet abundant rain in summer.

```{r Map,echo=FALSE,message=FALSE,warning=FALSE}
library(leaflet)

leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = 4.201,lat = 7.234)
```

The experiment was a factorial laid out in a RCBD with three replicates.

# Statistical analysis

The data collected was analyzed using analysis of variance (ANOVA) and significantly different means were seperated using Tukey's HSD at (P\<0.05).

# Result

50% of the females staying in the community are traders, 30% are teachers while 20% are farmers.

| Sex    | Occupation | Result |
|--------|------------|--------|
| Female | Trader     | 50     |
| Female | Teacher    | 30     |
| Female | Farmer     | 20     |

: Socio-economic characteristics of the female farmers

```{r}
Table2 <- tibble::tribble(
      ~Sex, ~Occupation, ~Result,
  "Female",    "Trader",      50,
  "Female",   "Teacher",      30,
  "Female",    "Farmer",      20
  )

require(knitr)
kable(Table2, digits = 3, row.names = FALSE, align = "c",
              caption = 'Socio Economic Characteristics of the farmer')

```

# Discussion

# Conclusion

# Acknowlegement

\newpage

**References**
