---
title: "Report Writting in R"
author: "Oluwafemi Oyedele"
date: '2022-03-10'
output:
  word_document:
   reference_docx: template.docx
bibliography: references.bib
---

# Abstract

# Introduction

Yam production in Nigeria is one of the largest agricultural produce [@pérez-flores2017a]. Knowing the nutrient composition of litter is useful for planning nutrient management of plantations [@bai2022leaf]. In Cocoa (*Theobroma* cacao\* L.) plantations, tree species are combined in different vertical strata [@fontes2014nutrient; @pérez-flores2017a]. Cocoa litter has a poor quality @fontes2014nutrient reported N rate in cocoa litter was low .

The objectives of this work is to identify the socio-economy characteristics of the farmers.

# Materials and Methods

Study area

The study was conducted in the ejido Miguel Hi dalgo. Climate is hot and wet abundant rain in summer.

```{r Map,echo=FALSE,message=FALSE,warning=FALSE}
library(leaflet)

leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = 4.201,lat = 7.234)
```

The experiment was a factorial laid out in a RCBD with three replicates.

# Statistical analysis

The data collected was analyzed using analysis of variance (ANOVA) and significantly different means were seperated using Tukey's HSD at (P\<0.05).

# Result

50% of the females staying in the community are traders, 30% are teachers while 20% are farmers.

| Sex    | Occupation | Result |
|--------|------------|--------|
| Female | Trader     | 50     |
| Female | Teacher    | 30     |
| Female | Farmer     | 20     |

: Socio-economic characteristics of the female farmers

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.cap='plot1'}
library(ggplot2)
ggplot(data=iris,aes(x=Sepal.Length,y=Sepal.Width))+geom_point()+
  geom_smooth()
```

# Discussion

The traders were selling agricultural produce for the farmers. 50% of the traders were female, 30% were teachers and 20% were farmers which shows that majority of the female living in the community were traders (Table 1) [@adebayo2020assessment].

According to plot1 the Sepal length has a strong negative relationship with Sepal Width.

# Conclusion

It is concluded that majority of the female traders focus more on agricultural produce.

# Acknowledgement

I am pleased to appreciate Prof Fatimah from University of Ibadan Nigeria for assisting me throughout the computation of this manuscript. I appreciate Dr Mr Femi for all hard work in encouraging me throughout the research.

\newpage

**References**
